### 2015-09-29 untitled.tex
edited untitled.tex

>>>>

The deferrable execution of a deferrable task imposes a scheduling penalty because one instance of a deferrable task can first defer defer its execution by some amount of time and for the next instance without any deferrable execution. The purpose of the period enforcer algorithm is to reduce such penalty. One of the main contributions in the report in \cite{Raj:suspension1991} is its Theorem 5, as follows:

\begin{quote}
Theorem 5 \cite{Raj:suspension1991}: A deferrable task that is schedulable under its worst-case conditions is also schedulable under the period enforcer algorithm.
\end{quote}
